Analysis of Cartesian Genetic Programming's Evolutionary Mechanisms

### 2013-06-20 CGP Journal/main.tex
Wrote abstract.  Only remaining section is scalability

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
TODO The abstract goes here.
\end{abstract}

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
Understanding how search operators interact with solution representation is
a critical step to search improvement.  For many search algorithms this may
be trivial, but in Cartesian Genetic Programming (CGP), and Genetic Programming (GP)
in general, the complex genotype to phenotype map makes achieving understanding
challenging.  By examining tuned parameter values, variant success on different
problem difficulties, node behavior, and offspring replacement properties we
seek to comprehend observed characteristics of CGP search.  We focus our study
around methods to prevent wasted CGP evaluations (\emph{Skip}, \emph{Accumulate},
and \emph{Single}) and methods to overcome CGP's search limitations imposed by
genome ordering (\emph{Reorder} and \emph{DAG}).

We find strong evidence that currently most CGP techniques evolve genomes that
are highly inactive, very redundant, and full of seemingly useless constants.
In some instances we found less than 1\% of the genome was actually required to
encode the evolved solution.
Without \emph{Reorder} or \emph{DAG} almost the entire latter portion of the genome
is never used by any ancestor of the evolved solution.  More generally, our
results lead us to conclude that \emph{Skip Reorder} and \emph{Single Reorder}
are most likely to solve hard problems in the least number of evaluations and
the least amount of time, respectively, with the least amount of degenerate
behavior.

\end{abstract}
